SiO Molecular Jets around young stars - A numerical perspective

### 2013-07-31 PAPER/ms_final_bv.tex
Added bib file

\section{Parameter Survey}
\begin{table*}
\centering
\caption{Summary from parameter runs}
\begin{tabular}{l | l | l | l | l | l }
\hline
Run & Cooling Mode & $\eta$ & $\beta$ & Peak Intensity [K] & FWHM at Bow
Shock \\
\hline\hline
adi1010 & Nil (Adiabatic) & 10 & 10 &&\\
pow1010 & Power law & 10 & 10 &&\\
atm1010 & Atomic & 10 & 10 &&\\
atm101 & Atomic & 10 & 1 &&\\
atm210 & Atomic & 2 & 10 &&\\
tab1010 & Tabulated & 10 & 10 &&\\
tab210 & Tabulated & 2 & 10&&\\
mol1010 & Molecular & 10 & 10&&\\
mol510 & Molecular & 5 & 10&&\\
\hline
\end{tabular}
\label{tab:result1}

\end{table*}

@@

\subsection{Molecular cooling and H$_2$ Chemistry}
figure nos. 2 --> Explain molecular cooling in more details. With the
mechanism of formation and destruction of HI, H2 and HII using
figures. 
\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/molcjet_310.png}
 \caption{Fraction of hydrogen species in the run with molecular
   cooling having $\eta$ = 3 and $\beta$ = 10.}
\label{grid}
\end{figure*}

@@

\subsection{SiO Abundance profile}
figure nos. 2 -- Comparison of three profiles for SiO Abundance,
Contour maps for two transitions for top hat profile.

@@

Table 1 -- Parameter runs with changing $\beta$ (magnetic fields) and
$\eta$ (density contrast) for cooling \\
Results should have Peak Intensity after convolution., FWHM at tip of
bow shock.\\
Our reference run -- $\beta$ = 10.0, $\eta$ = 2.0, with cooling and
velocity dependent SiO Abundance. \\
Figure 3 -- Output from MHD simulations (Reference run).\\
Figure 4 -- Output from Rad Transfer (Reference run). Integrated
Intensity Maps for different transitions for three different cooling prescribtions. (TODO : TOM)\\
Figure 5 -- Spectra for the reference runs all transitions. (TODO :
TOM)\\
Figure 6 -- PV diagrams (TODO : TOM) for one transition in two directions.
Figure 7 -- Angle of Inclination dependence

@@

Effects of varing abundance profile ... Crucial ingredient in
modeling molecular bullets \\
\begin{figure}
 \includegraphics[width=1.\columnwidth]{\figpath/EM_diffabun.png}
 \caption{Variation of 2-$>$1 SiO emission for runs with molecular
   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance profiles.}
\label{grid}
\end{figure}

@@

Advantage of non-LTE modeling over LVG Cabrit 2007, Lee 2008. 
Line ratios $\sim$ 1 can be explained well. \\
\begin{figure}
 \includegraphics[width=1.\columnwidth]{\figpath/LineRatio_TH_60_Y205.png}
 \caption{{\em{Top}} Line profiles in SiO J = 2-1, 5-4 and 8-7 at one
   the inner knot for the molecular cooling run with $\eta$ = 3 and
   $\beta$ = 10 using top hat abundance profile. The profiles are
   obatined when the angle of inclination is 60$^{\circ}$ with respect
 to line of sight. {\em{Bottom}} Line temperature ratios T(8-7)/T(5-4)
and T(2-1)/T(5-4), as a function of velocity}
\label{grid}
\end{figure}

>>>>

\section{Parameter Survey}
\begin{table*}
\centering
\caption{Summary from parameter runs}
\begin{tabular}{l | l | l | l | l | l }
\hline
Run & Cooling Mode & $\eta$ & $\beta$ & Peak Intensity [K] & FWHM at Bow
Shock \\
\hline\hline
adi1010 & Nil (Adiabatic) & 10 & 10 &&\\
pow1010 & Power law & 10 & 10 &&\\
atm1010 & Atomic & 10 & 10 &&\\
atm101 & Atomic & 10 & 1 &&\\
atm210 & Atomic & 2 & 10 &&\\
tab1010 & Tabulated & 10 & 10 &&\\
tab210 & Tabulated & 2 & 10&&\\
mol1010 & Molecular & 10 & 10&&\\
mol510 & Molecular & 3 & 10&&\\
\hline
\end{tabular}
\label{tab:result1}
\end{table*}

@@

\subsection{Molecular cooling and H$_2$ Chemistry}
In case of molecular outflows, the most appropiate form of cooling
prescribtion among the ones described in sect.~\ref{sec:chem} is
that which involves the evolution of H$_2$ chemistry along with
contributions to cooling from fixed fractions of other molecules like
CO, OH etc. Figure~\ref{fig:Hfracsim} shows the density of
various hydrogen species in the outflow. Also shown in the figure is
the temperature and mean molecular weight $\mu$. As the jet propgates
into the medium

figure nos. 2 --> Explain molecular cooling in more details. With the
mechanism of formation and destruction of HI, H2 and HII using
figures. 
\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/molcjet_310.png}
 \caption{Fraction of hydrogen species in the run with molecular
   cooling having $\eta$ = 3 and $\beta$ = 10.}
\label{fig:Hfracsim}
\end{figure*}

@@

\subsection{SiO Abundance profile}
figure nos. 2 -- Comparison of three profiles for SiO Abundance,
Contour maps for two transitions for top hat profile.
\begin{figure}
 \includegraphics[width=1.\columnwidth]{\figpath/EM_diffabun.png}
 \caption{Variation of 2-$>$1 SiO emission for runs with molecular
   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance profiles.}
\label{grid}
\end{figure}

@@

@@

Effects of varing abundance profile ... Crucial ingredient in
modeling molecular bullets \\

@@

Advantage of non-LTE modeling over LVG \cite{Cabrit:2007p13804}, \cite{Lee:2008p13697}. 
Line ratios $\sim$ 1 can be explained well for low mass stars and 
\cite{Leurini:2013p13165} for high mass stars. \\
\begin{figure}
 \includegraphics[width=1.\columnwidth]{\figpath/LineRatio_TH_60_Y205.png}
 \caption{{\em{Top}} Line profiles in SiO J = 2-1, 5-4 and 8-7 at one
   the inner knot for the molecular cooling run with $\eta$ = 3 and
   $\beta$ = 10 using top hat abundance profile. The profiles are
   obatined when the angle of inclination is 60$^{\circ}$ with respect
 to line of sight. {\em{Bottom}} Line temperature ratios T(8-7)/T(5-4)
and T(2-1)/T(5-4), as a function of velocity}
\label{grid}
\end{figure}
